AUTOMATED TRANSCRIPTION OF DRUMSOUNDS

### 2017-08-18 Latex/Paper/main.tex
Overall corrections

\begin{minipage}[b]{1.0\linewidth}
  \centering
  \centerline{\includegraphics[width=6.7cm]{figures/ActivationMatrix}}
%  \vspace{2.0cm}
  \medskip
\end{minipage}

@@

\begin{align}
\label{eq:timePoint}
timePoint = zeroCrossingFrameNumber * \frac{hopSize}{f_s}
\end{align}

Due to the formula \ref{eq:timePoint} we are only able to get the time point within a range of approx. 12 ms (called epsilon).
Once this calculation is done we receive a list of time points where the given template is found in the song which is the drum transcription we were looking for.

@@

As mentioned above he precision of the detected peak time point is only precise within a range of approx. 12 ms since only the STFT frame it occurring in can be tracked.
The precision could be improved by using a sinc interpolation to exactly determine the point of inflection.

>>>>

\begin{minipage}[b]{1.0\linewidth}
  \centering
  \centerline{\includegraphics[width=8.5cm]{figures/ActivationMatrix}}
%  \vspace{2.0cm}
  \medskip
\end{minipage}

@@

\begin{align*}
\label{eq:timePoint}
timePoint = zeroCrossingFrameNumber * \frac{hopSize}{f_s}
\end{align*}

Due to this formula we are only able to get the time point within a range of approx. 12 ms (called epsilon).
Once this calculation is done we receive a list of time points where the given template is found in the song which is the drum transcription we were looking for.

@@

As mentioned above the precision of the detected peak time point is only precise within an epsilon range of approx. 12 ms since only the STFT frame it occurring in can be tracked.
By interpolating between nearby frames the accuracy of the point of inflection could be improved making the epsilon range significant smaller.
